sensi_an_rotations1. Start of sensitivity analysis for rotations.

### 2018-07-11 inst/documents/rotations_notes.Rmd
adding mutation-selection balance

@@

>>>>

*9/7/18* mutation-seln balance

not quite working in run_rot() yet

run_rot(no_r_below_start=FALSE,no_r_below_mut = TRUE)

Ian said that mutation rate of 10e-9 is used in malaria studies. John Maynard Smith, Evolutionary Genetics p62 suggests mutation rate per generation per locus from drosophila of 10e-6.

Ian suggested that he expected these frequencies to be so low that using them as a lower limit will not effect simulations.

Checking ability to do runs where insecticides differ.
Code at end of sensi_an_rotations1

Currently getting these warnings, & seemingly more rows than scenarios in df_res_all ...
1: In if (dom_cos == 0) { ... :
  the condition has length > 1 and only the first element will be used

fixed vectorising mutn_seln_bal.r

Running for insecticides with different inputs now works :
dfr <- run_rot(n_insecticides=3, eff=c(1,0.6,0.4), rot_interval=0)

but I don't get one row per scenario in df_res_all from sensi_an_rotations

for 10 runs I get 31 rows
because I'm getting 1 row per insecticide in each run
where does that happen ?
seems it happens in this line :

df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq))

when linputs contains some elements that are vectors (repeated for each insecticide) the resulting dataframe has one row per insecticide.

I would rather have one row per scenario and have all the vector elements saved to one record, perhaps as a comma delimited string ?

seems that as.data.frame is the culprit. what about tidyverse option ? no didn't work

this is the issue I have :
as.data.frame(c(double=c(9,6), single=7))

converts to this :
double1                               9
double2                               6
single                                7

when I want something like 
double1                               9,6
single                                7

@@

~ ian interested in starting frequencies at 10e-4, can do that for the runs with different values per insecticide.
~ ian suggested talking to Simon if we need to run something for longer

1. check out these runs that have the mut-sel balance option enabled
df_res_all_rot_cost10000_mut_sel_bal.rda
2. check ability to do runs where insecticides differ

Currently getting these warnings, & seemingly more rows than scenarios in df_res_all ...
1: In if (dom_cos == 0) { ... :
  the condition has length > 1 and only the first element will be used

~ think - are all rotation runs so far based on insecticides with equal effectiveness, resistance restoration, cost etc. ? What might happen if we allow differences between insecticides ? Can we easily represent that ?
I could possibly run one set of simulations where insecticides are allowed to be different.
I think that could be set up by changing :
linputs$expo_hi <-  runif(1, min=0.4, max=0.9)
to:
runif(n_insecticides, min=0.4, max=0.9)
This might break stuff.
Can just check that prop runs in which rotations are better doesn't increase.
I suspect input params may be saved to outfiles as comma delimited strings ?

### 2018-07-11 inst/documents/sensi_an_rotations1.Rmd
adding mutation-selection balance

# set random seed so that results can be reproduced
#set.seed(1)
set.seed(2)
max_gen         <- 500
plot_scenarios  <- FALSE
n_scenarios     <- 10000 
already_ran     <- FALSE
#already_ran     <- TRUE

@@

    #beware min_rwr_interval, it's to stop repeated small rotations
    linputs$min_rwr_interval <- 5
    linputs$min_gens_switch_back <- 1
    linputs$no_r_below_start <- FALSE #BEWARE this has been set to TRUE in all earlier runs
    #set plot to F if using grid.arrange as in phaps-rotations-better.Rmd
    linputs$plot <-     FALSE

@@

    # add scenario id column onto results
    res$scenario <- i
    df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq))
    df_in_out$rot_minus_seq <- df_in_out$gens_rot - df_in_out$gens_seq

@@

>>>>

# set random seed so that results can be reproduced
#set.seed(1)
set.seed(2)
max_gen         <- 500
plot_scenarios  <- FALSE
n_scenarios     <- 10 #000 
already_ran     <- FALSE
#already_ran     <- TRUE

@@

    #beware min_rwr_interval, it's to stop repeated small rotations
    linputs$min_rwr_interval <- 5
    linputs$min_gens_switch_back <- 1
    linputs$no_r_below_start <- FALSE #BEWARE this has been set to TRUE in all earlier runs
    linputs$no_r_below_mut <- TRUE #BEWARE trying out new mutation-selection balance option
    #set plot to F if using grid.arrange as in phaps-rotations-better.Rmd
    linputs$plot <-     FALSE

@@

    # add scenario id column onto results
    # this isn't doing anything
    # res$scenario <- i
    df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq))
    df_in_out$rot_minus_seq <- df_in_out$gens_rot - df_in_out$gens_seq

@@

# Have a go at running for insecticides with different parameters

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=11, comment=NA}

# set random seed so that results can be reproduced
set.seed(2)
max_gen         <- 500
plot_scenarios  <- FALSE
n_scenarios     <- 10 #000

  df_res_all <- data.frame()

    #beware min_rwr_interval, it's to stop repeated small rotations
    linputs$min_rwr_interval <- 5
    linputs$min_gens_switch_back <- 1
    linputs$no_r_below_start <- FALSE #BEWARE this has been set to TRUE in all earlier runs
    linputs$no_r_below_mut <- TRUE #BEWARE trying out new mutation-selection balance option
    #set plot to F if using grid.arrange as in phaps-rotations-better.Rmd
    linputs$plot <-     FALSE

    ## variable inputs ##
    linputs$n_insecticides <- sample( 2:5, 1 )  #beware set replace=T if more than 1
    n_ins <- linputs$n_insecticides

    ## new those below can be different for each insecticide
    linputs$cost <-           runif(n_ins, min=0,   max=0.1) 
    #linputs$cost <-           0 
    linputs$expo_hi <-        runif(n_ins, min=0.4, max=0.9)  #min=0.1, max=0.9
    linputs$male_expo_prop <- runif(1, min=0,   max=1)
    linputs$eff <-            runif(n_ins, min=0.5, max=1) # min=0.3, max=1
    linputs$rr  <-            runif(n_ins, min=0.1, max=0.9)
    linputs$dom_sel <-        runif(n_ins, min=0,   max=1)
    linputs$dom_cos <-        runif(n_ins, min=0,   max=1) 
    linputs$start_freqs <-    runif(n_ins, min=0.005,   max=0.1) #note not log yet

    # dispersal (initially with cost set to 0)
    #linputs$coverage <-       runif(1, min=0.1, max=0.9)
    #linputs$migration <-      runif(1, min=0.1, max=0.9)

        # to plot results for checking
        if ( linputs$rot_interval == 0 )
        {
          ggseq <- ggres
          gens_seq <- as.numeric(res)
        } else
        {
          ggrot <- ggres
          gens_rot <- as.numeric(res)
        }
      }
    } #end rot_or_not loop

    # add scenario id column onto results
    # this isn't doing anything
    # res$scenario <- i
    df_in_out <- as.data.frame(c(linputs, gens_rot=gens_rot, gens_seq=gens_seq))
    df_in_out$rot_minus_seq <- df_in_out$gens_rot - df_in_out$gens_seq
